---
title: "Homework: Reproducibility and Professional Communication"
execute:
  error: true
author: "Lucia Bonfanti"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 3)
```


# Reproducible Examples & Debugging

In the following examples, evaluate each problem using the criteria of a minimal reproducible example from [this StackOverflow post](https://stackoverflow.com/help/minimal-reproducible-example). 

Specifically, address the following things: 

1. Are the question and problem description complete?

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

3. Is the example minimal? Does it include extra code or information that is not necessary?

4. Does the question describe any attempted solutions?


Then, using what you know about R and Python, try to debug the problem using the strategies in [the debugging chapter](https://srvanderplas.github.io/stat-computing-r-python/part-gen-prog/06-debugging.html). Once you are thoroughly stumped, or you believe you have solved the problem, compare your solutions to those given on StackOverflow using the link.

## Why Doesn't this R function work?

> I created the following function to append new strings on a vector of strings called "meals". However, when I use this function to append an string input into my "meals" vector, it does not work.

```{r setup, include=FALSE}
 add <- function(str) {
      meals <- append(meals, as.character(str))  
 }

```

[Link](https://stackoverflow.com/questions/39795961/why-doesnt-this-r-function-work?noredirect=1&lq=1) to original SO post. 


---

1. Are the question and problem description complete?
No, I think he will have to put what the meals where to understand better the code. 


2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

The function is reproducible, but when you put add ("") it will not reproduce, so is not reproducible because it said that object meals is not found, so when I try add it gives me an error of 
"Error in add("chicken") : object 'meals' not found."

3. Is the example minimal? Does it include extra code or information that is not necessary?

Yes, it is minimal. It don't include extra code or information that is not necessary. 

4. Does the question describe any attempted solutions?

No, do not describe In the following examples, evaluate each problem using the criteria of a minimal reproducible example from [this StackOverflow post](https://stackoverflow.com/help/minimal-reproducible-example). 

Specifically, address the following things: 

1. Are the question and problem description complete?

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

3. Is the example minimal? Does it include extra code or information that is not necessary?

4. Does the question describe any attempted solutions?


Then, using what you know about R and Python, try to debug the problem using the strategies in [the debugging chapter](https://srvanderplas.github.io/stat-computing-r-python/part-gen-prog/06-debugging.html). Once you are thoroughly stumped, or you believe you have solved the problem, compare your solutions to those given on StackOverflow using the link.

## Why Doesn't this R function work?

> I created the following function to append new strings on a vector of strings called "meals". However, when I use this function to append an string input into my "meals" vector, it does not work.

```{r setup, include=FALSE}
 add <- function(str) {
      meals <- append(meals, as.character(str))  
 }

```

[Link](https://stackoverflow.com/questions/39795961/why-doesnt-this-r-function-work?noredirect=1&lq=1) to original SO post. 


---

1. Are the question and problem description complete?
No, I think he will have to put what the meals where to understand better the code. 


2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

The function is reproducible, but when you put add ("") it will not reproduce, so is not reproducible because it said that object meals is not found, so when I try add it gives me an error of 
"Error in add("chicken") : object 'meals' not found."

3. Is the example minimal? Does it include extra code or information that is not necessary?

Yes, it is minimal. It don't include extra code or information that is not necessary. 

4. Does the question describe any attempted solutions?

No


## Function not working R

> I've never programmed before and am trying to learn. I'm following that "coursera" course that I've seen other people post about — a course offered by Johns Hopkins on R programming.

> Anyway, this was supposed to be my first function. Yet, it doesn't work! But when I type out all the steps individually, it runs just fine... Can anyone tell me why?

```{r setup, include=FALSE}
pollutantmean <- function(directory, pollutant, id = 1:332){
    x<- list.files("/Users/mike******/Desktop/directory", full.names=TRUE)
    y<- lapply(x, read.csv)
    z<- do.call(rbind.data.frame, y[id])

    mean(z$pollutant, na.rm=TRUE)
}
pollutantmean(specdata,nitrate,1:10)
[1] NA
Warning message:
In mean.default(z$pollutant, na.rm = TRUE) :
  argument is not numeric or logical: returning NA

####

x<- list.files("/Users/mike******/Desktop/specdata",full.names=TRUE)
y<- lapply(x,read.csv)
z<- do.call(rbind.data.frame,y[1:10])
mean(z$nitrate,na.rm=TRUE)
[1] 0.7976266
```


[Link](https://stackoverflow.com/questions/24123224/function-not-working-r/24141502)


---

1. Are the question and problem description complete?

No, he have to describe more the problem and the type of output he want to get with all that code. 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

No, because the file is in his Desktop. No, he don't have a description of the problem. Just show the warning message but did not explain enough. I think it will help if he has a problem description complete

3. Is the example minimal? Does it include extra code or information that is not necessary?

NO, it include extra information. 

4. Does the question describe any attempted solutions?

No


## Inexplicable error when trying to export my R notebook

> Getting this error from R Markdown when trying to export my .RMD

```
"Error in filter(Gastropods, Species == "Cellana") :  object 'Species' not found Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> filter"
```

> However, all my plots are coming out successfully. I can clearly see in the data that the species column is there and that Cellana is a species. No spelling errors or anything.

> My first 20 or so lines of code are below (between the ### symbols)


````{r echo=FALSE}
cat(paste(readLines("https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt"), collapse = '\n'))
````

You can find this sample file [here](https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt)


[Link](https://stackoverflow.com/questions/44193367/inexplicable-error-when-trying-to-export-my-r-notebook)

---

1. Are the question and problem description complete?

Yes, they are complete 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

No, because we don't have the file it used. Yes, it have the description of the problem. It will improve it takes the unnecessary codes. 

3. Is the example minimal? Does it include extra code or information that is not necessary?

Is not minimal, it include extra code. 

4. Does the question describe any attempted solutions?

Yes, it checked on spelling errors


## Python if elif else statement

> I'm trying to create a program with python that calculate the cost for shipping.

> However, I can't run the program to where it works properly.

> What ever my total is the same amount comes out as $6 for US and $8 for Canada. I can't seem to get pass that.

> Example:

```{python solo-fizzbuzz-py, echo = T} 
total = raw_input('What is the total amount for your online shopping?')
country = raw_input('Shipping within the US or Canada?')

if country == "US":
    if total <= "50":
        print "Shipping Costs $6.00"
    elif total <= "100":
            print "Shipping Costs $9.00"
    elif total <= "150":
            print "Shipping Costs $12.00"
    else:
        print "FREE"

if country == "Canada":
    if total <= "50":
        print "Shipping Costs $8.00"
    elif total <= "100":
        print "Shipping Costs $12.00"
    elif total <= "150":
        print "Shipping Costs $15.00"
    else:
        print "FREE"
```


[Link](https://stackoverflow.com/questions/19371643/python-if-elif-else-statement)

---

1. Are the question and problem description complete?

Yes, they are describe complete the question and the problem. 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

No, because we do not have the files of 'What is the total amount for your online shopping?' and 'Shipping within the US or Canada?'. Yes, it has a description of the problem. 


3. Is the example minimal? Does it include extra code or information that is not necessary?

Yes, it is minimal. Do not include an extra code or information that is not necessary. 

4. Does the question describe any attempted solutions?

NO, it does not describe any attemped solutions. 



## Function not working R

> I've never programmed before and am trying to learn. I'm following that "coursera" course that I've seen other people post about — a course offered by Johns Hopkins on R programming.

> Anyway, this was supposed to be my first function. Yet, it doesn't work! But when I type out all the steps individually, it runs just fine... Can anyone tell me why?

```{r setup, include=FALSE}
pollutantmean <- function(directory, pollutant, id = 1:332){
    x<- list.files("/Users/mike******/Desktop/directory", full.names=TRUE)
    y<- lapply(x, read.csv)
    z<- do.call(rbind.data.frame, y[id])

    mean(z$pollutant, na.rm=TRUE)
}
pollutantmean(specdata,nitrate,1:10)
[1] NA
Warning message:
In mean.default(z$pollutant, na.rm = TRUE) :
  argument is not numeric or logical: returning NA

####

x<- list.files("/Users/mike******/Desktop/specdata",full.names=TRUE)
y<- lapply(x,read.csv)
z<- do.call(rbind.data.frame,y[1:10])
mean(z$nitrate,na.rm=TRUE)
[1] 0.7976266
```


[Link](https://stackoverflow.com/questions/24123224/function-not-working-r/24141502)


---

1. Are the question and problem description complete?

No, he have to describe more the problem and the type of output he want to get with all that code. 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

No, because the file is in his Desktop. No, he don't have a description of the problem. Just show the warning message but did not explain enough. I think it will help if he has a problem description complete

3. Is the example minimal? Does it include extra code or information that is not necessary?

NO, it include extra information. 

4. Does the question describe any attempted solutions?

No


## Inexplicable error when trying to export my R notebook

> Getting this error from R Markdown when trying to export my .RMD

```
"Error in filter(Gastropods, Species == "Cellana") :  object 'Species' not found Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> filter"
```

> However, all my plots are coming out successfully. I can clearly see in the data that the species column is there and that Cellana is a species. No spelling errors or anything.

> My first 20 or so lines of code are below (between the ### symbols)


````{r echo=FALSE}
cat(paste(readLines("https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt"), collapse = '\n'))
````

You can find this sample file [here](https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt)


[Link](https://stackoverflow.com/questions/44193367/inexplicable-error-when-trying-to-export-my-r-notebook)

---

1. Are the question and problem description complete?

Yes, they are complete 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

No, because we don't have the file it used. Yes, it have the description of the problem. It will improve it takes the unnecessary codes. 

3. Is the example minimal? Does it include extra code or information that is not necessary?

Is not minimal, it include extra code. 

4. Does the question describe any attempted solutions?

Yes, it checked on spelling errors


## Python if elif else statement

> I'm trying to create a program with python that calculate the cost for shipping.

> However, I can't run the program to where it works properly.

> What ever my total is the same amount comes out as $6 for US and $8 for Canada. I can't seem to get pass that.

> Example:

```{python solo-fizzbuzz-py, echo = T} 
total = raw_input('What is the total amount for your online shopping?')
country = raw_input('Shipping within the US or Canada?')

if country == "US":
    if total <= "50":
        print "Shipping Costs $6.00"
    elif total <= "100":
            print "Shipping Costs $9.00"
    elif total <= "150":
            print "Shipping Costs $12.00"
    else:
        print "FREE"

if country == "Canada":
    if total <= "50":
        print "Shipping Costs $8.00"
    elif total <= "100":
        print "Shipping Costs $12.00"
    elif total <= "150":
        print "Shipping Costs $15.00"
    else:
        print "FREE"
```


[Link](https://stackoverflow.com/questions/19371643/python-if-elif-else-statement)

---

1. Are the question and problem description complete?

Yes, they are describe complete the question and the problem. 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

Yes, no extenral files. Yes, it has a description of the problem. 


3. Is the example minimal? Does it include extra code or information that is not necessary?

Yes, it is minimal. Do not include an extra code or information that is not necessary. 

4. Does the question describe any attempted solutions?

NO, it does not describe any attemped solutions. 


# Professional Communication

## Slides

Create a set of quarto slides in the file slides.qmd. 

Set two different output formats - for instance, reveal.js and beamer. 

In your slides:

- Introduce yourself and show a picture of yourself
- Provide basic biographical information: birthday, where you grew up
- Show a picture of your favorite animal
- Provide your favorite plot, generated in either R or python. (This can be one you've generated in this class). Ensure that the code does not show, but the plot does.
- Provide a link to your CV, which you will generate in the next part.

## CV

Select a CV template that uses either LaTeX or Markdown:

- https://github.com/kazuyanagimoto/quarto-awesomecv-typst
- https://github.com/schochastics/quarto-cv
- https://www.overleaf.com/latex/templates/tagged/cv

Use the template to create a curriculum vitae that has your education, work experience, and any other sections you would like to include. Compile your CV and link to it in your slides. 
